True versus apparent shapes of astrophysical bow shocks

### 2017-04-19 papers/Paper1/quadrics-appendix.tex
Yet more fiddling with big p-value table
I decided to reverse the sign of Cohen's d for consistency with the
rank biserial correlation coefficient.  Also turn the sig/tau value
upside down so that it is usually bigger than one.  The table is now
generated automatically from the JSON file, so any further adjustments
will be easy.

From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$

@@

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
  (b)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
    tests performed during the analysis of
    section~\ref{sec:comp-with-observ}. (a)~Uniformly spaced linear
    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
    bins and logarithmic vertical axis, with all values
    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
    lines shows the traditional threshold values for significance:
    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
    uniform distribution of \(p\)-values that would be expected if the
    null hypothesis were always true, that is, if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

>>>>

From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
\clearpage

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\addtocounter{section}{-1}

@@

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
  (b)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
    bins and logarithmic vertical axis, with all values
    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
    lines shows the traditional threshold values for significance:
    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
    uniform distribution of \(p\)-values that would be expected if the
    null hypothesis were always true, that is, if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
